We need to beat namespotting, no idea how

### 2023-01-17 paperSubmission/paperSubmission1.tex
added three sections

\section{Counter-speech interventions}
%counter-speech def

@@

>>>>

\section{Automated versus human-based moderation}\label{sec:automated-versus-human}

The hindrances and threats that go along with the Artificial Intelligence-based methods for moderation have been widely debated, with the most critical discussions revolving around the technology performance \citep{macavaney2019hate, schmidt2017survey}. 
State-of-the-art solutions are mostly governed by statistical methods, including deep learning and machine learning \citep{jordan2015machine, lecun2015deep, sejnowski2020unreasonable}. Their performance is inherently tied to the amount of data being fed to the system and annotation quality.

At different stages of the process, from data gathering and preparation, annotation,  to the training or algorithms themselves, biases seem to be omnipresent \citep{binns2017like, geva2019we, mehrabi2021survey}. For instance, \citet{sap_risk_2019} examined how the lack of knowledge of data annotators about the dialect of minorities can lead to the amplification of bias against those minorities. When improperly trained, annotators repeatedly make incorrect judgments about comments expressed in African American English dialect, those mistakes are repeated by algorithms once the model learns to identify hate speech using such datasets. Since algorithms are getting more control in the decision-making process of who can participate in discussions online, such errors can have detrimental effects on people of African-American descent, who can be excluded from certain communities.

Yet another bias can result from the technical shortcomings of statistical methods such as deep learning and machine learning. For instance, Perspective API,\footnote{\url{https://perspectiveapi.com}} a tool for detection of verbal aggression online, was repeatedly judging neutral sentences such as: “I am a woman”, “I am a Jew”, or “I am a black gay woman”, as highly toxic \citep{jigsaw2019}. Such errors are inextricably related to the foundations of deep learning and machine learning models, which learn directly from the annotated data. Since women and minorities are frequently a target of attacks, such algorithms, which have no understanding about the structure of the sentence and the grammar behind it, make statistical approximation and incorrectly give a high toxicity score because of the occurrence of “sensitive” keywords—woman, Jew, black, gay, and so on.

Users of online services are also creative in their strategies of circumventing automated content moderation systems, and as shown by \citet{grondahl2018all}, current techniques are vulnerable to the most common evasions such as word changes (inserting typos and leetspeak), word-boundary changes (inserting or removing whitespace), or word appending (appending common or non-hateful words). For instance, in the evaluation of seven state-of-the-art models trained for hate speech detection, adding “love” to abusive sentences---a word which is negatively correlated with hate speech---resulted in the F1 score\footnote{This is  an overall measure of a model’s accuracy that combines precision and recall.} preformance decrease to almost  0\% in the majority of models tested.

Lack of generalizability of the models---the ability to perform well on datasets coming from sources other than the one used for training---is a severe shortcoming as well \citep{rosa2019automatic, yin2021towards}. As shown again by \citet{grondahl2018all}, models trained on a dataset coming from Wikipedia, which achieve 86\% of F1 score, perform below 50\% F1 on Twitter (between 24\% to 50\% depending on the model and the Twitter sample). The adaptability from Twitter to Wikipedia looks even worse. One of the models trained on a Twitter sample with a performance of 83\% F1 dropped to 14\% on a Wikipedia sample.

As shown by \citet{wu2019errudite, lipton2019troubling, musgrave2020metric} in practice, the development of such models often lacks thorough error analysis and legitimate experimental methodology, which can result in non-reproducibility. This is also connected with a potential lack of thorough understanding of the limitations of the models and spurious conclusions being announced to a wider public. Specifically, \citet{lipton2019troubling} distinguishes four dysfunctional patterns occurring in the current research paradigm in the industry and academia alike:

\begin{enumerate}
    \item First, the inability to draw a clear distinction between speculation and explanation, with the former often being disguised as the latter. For instance, in \citet{steinhardt2017certified} the author admitted to stating that “the high dimensionality and abundance of irrelevant features...give the attacker more room to construct attacks”---although no experiments were conducted to measure the effect of dimensionality of the neural network on its attackability.
    \item Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect). As was shown by \citet{melis2017state}, some improvements in language modeling, which originally were ascribed to complex innovations in the architecture of the network, stem from hyperparameter tuning. As mentioned by \citet{lipton2019troubling}, there is a tremendous value coming from the thorough understanding of a particular method, and a variety of techniques are vital in the process (like ablation, robustness checks, qualitative error analysis) for the benefit of the whole community.
    \item Third, “mathiness”---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon. Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang \citet{steinhardt2015learning} with an irrelevant theorem to amplify the empirical results. They discussed “staged strong Doeblin chains” which actually had limited pertinence to the learning algorithm, which was the main subject of a paper.
    \item Last but not least, misuse of language. This includes suggestive definitions without proper explanations of what they mean in the context (e.g., calling good performance in simple NLP tasks a human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g. consciousness). In one of the examples described, empirical results reported by \citet{esteva_dermatologist-level_2017} in which a classifier achieved low error on independent and identically distributed test data was described as “dermatologist-level classification of skin cancer,” omitting the fact that dermatologists judge cases of much wider variety.
\end{enumerate}

Yet another obstacle in the process is the lack of gold standard in dataset construction and taxonomies of abusive language being used, for instance, in the process of annotating different datasets. Frequently people obtain data from various sources and do not follow any universally used instructions when it comes to annotation, what results in lack of annotation coherency across various datasets related to one phenomenon (e.g., hate speech). The lack of expert annotators and proper annotation criteria and instructions are also widespread, with the common practice of hiring untrained workers from Mechanical Turk or other crowdsourcing platforms.

Although there are some initiatives developed in response, most notably, functional tests for Hate Speech Detection Models created by \citet{rottger2020hatecheck}, or the Online Safety Data Initiative (OSDI) \citep{onlinesafetydata}, focused on projects related to improving access to data, standardizing the description of online harms, as well as creating tools and benchmarks for evaluation of technologies focused on safety, much effort must be made before wider adoption of such solutions comes into force.

At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms. On Facebook, there are more than 3B comments and likes daily \citep{noauthor_facebook:_2012}, 500M tweets are sent daily on Twitter \citep{noauthor_10_2021}, and over 2B comments made by users of Reddit in 2020 \citep{noauthor_reddit_nodate}, which is almost 3M comments made daily. With this amount of content, it’s either impossible or extremely costly to scale the moderation workforce. One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being. Being submersed in the cyber-Augean stables takes a toll on many---as examined by \citet{roberts2014behind, roberts2016commercial}. Workers hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they’ve seen in secret under restrictive NDAs. This in turn, makes the research in the area extremely difficult, since moderators are not allowed to talk about their work conditions or any other related subject. Those who decide to break the NDA risk a penalty.

Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases. This can lead to serious psychological damage, such as depression or PTSD \citep{roberts2014behind}. Although there are certain initiatives being developed or introduced to reduce the emotional impact of the moderation, such as stylistic alterations to  content (for instance, applying grayscale or blurring to images
 \citep{karunakaran2019testing}, workplace wellness programs, clinical support, or psychological training \citep{steiger2021psychological}, none of the methods can eliminate the psychological distress completely. Some of the employees filed a lawsuit against Facebook, and as a result, the company agreed to pay \$52M in compensation for mental health issues developed during the job \citep{newton_facebook_2020}. Also, as described by \citet{parks2019dirty}, the work is often performed under time pressure, reviewing 25K pieces of content per day. Spending on average three to five seconds on each image reported for moderation might not lead to the most thoughtful decisions, and as shown by \citet{stepanikova2012racial}, high time pressure can amplify human biases. Considering that Facebook employs 15K moderators \citep{koetsier_report} and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a carefully thought-out collaboration between humans and machines in this area seems indispensable and highly demanded.

\section{Different approaches to content moderation}\label{sec:content-moderation}

There are different approaches when it comes to the moderation of online content. One can follow the workflow of reactive moderation, which happens once the content is published. Harmful messages can be either reported by the users of the platforms or identified by automated methods and then sent for review to moderators. A set of actions can then be taken depending on the platform, its community guidelines, on the content, or on the user level. A harmful message can be deleted, made invisible to other users, or certain profanities can be altered with special signs to censor them. Depending on the type and amount of infraction, a particular user can be warned, muted, shadowbanned, or banned from further participation in the community for a period of time. The weakness of the reactive method is that the damage is already done. Whoever is the recipient of the abusive message has the chance to see it and potentially suffer \citep{hoff2009cyberbullying, keipi2016online, wachs2019associations}. Yet another weakness connected with relying solely on human reports is the content that is harmful but unreported by its recipient or bystanders. Although the exact scale of unreported negative content is not known, various self-report studies show that a lot of children, teens, or even adults do not report cyberbullying or harassment online \citep{french_as_2021, ADL_free, noauthor_:game_nodate}.

Yet another type of moderation is pro-active moderation. On this approach, automated methods used are either based on Artificial Intelligence or other less sophisticated tools (e.g., blacklists) and can screen the content before it gets published. If a harmful message is detected, it can be removed before reaching the recipient. Due to the aforementioned dubious performance of state-of-the-art statistical methods, particularly low precision, such tools are rarely used autonomously, and serve as additional support to content moderators. Alternatively, all content can be reviewed by moderators before it gets published on a website, although such a process is rarely implemented, as it stifles the discussion.

Another categorization can be obtained by looking at who is engaged in the moderation of the content. In a distributed or decentralized moderation system, the community members decide which content gets taken down, as opposed to a centralized moderation system, in which professionals hired by a particular service are in charge. Some services use a hybrid approach, with Reddit being one of such cases. Consisting of numerous communities initiated by Reddit's users, the owners of the so-called subreddits (mods) are in control of the moderation within the subreddit. At the same time, Reddit hires a small centralized team of moderators (admins) that enforce content policy on a broader scale.

\section{Counter-speech interventions}\label{sec:counter-speech}
%counter-speech def

@@

\section{Technology applied for personal attack detection}
\label{sec:technology}

To perform the research at a scale sufficient for statistically reliable analysis, we needed to apply a technology for the initial automatic detection of personal attacks, to be further forwarded to human moderators for deeper analysis and making decisions regarding the outcome of the moderation (e.g., deletion of the post, sending a warning to an abusive user, banning the user, etc.). As we already mentioned in sections \ref{sec:automated-versus-human}, \ref{sec:content-moderation} and \ref{sec:collective-intelligence}, performing the moderation relying on the assumption that the moderator will read through all of the posts and comments is unrealistic, while moderation based solely on  other users' reporting could lead to a large number of abusive messages remaining unreported. This problem, present   in the literature \citep{ptaszynski2018automatic,urbaniak2022personal} and in  the mass media\footnote{\url{https://www.japantimes.co.jp/news/2022/12/03/business/tech/twitter-harmful-content/}}\textsuperscript{,}\footnote{\url{https://www.forbes.com/sites/forbestechcouncil/2022/06/14/the-growing-role-of-ai-in-content-moderation/}} has lead to an increase in the number or automatic tools being developed  and deployed to support content moderators in their work.\footnote{\url{https://influencermarketinghub.com/content-moderation-tools/}.}

In our research  we applied Samurai detection software, a
proprietary technology developed Samurai Labs.\footnote{\url{https://www.samurailabs.ai/},
  described in (Ptaszyński, Leliwa, Piech, \& Smywiński-Pohl, 2018;
  Wroczynski \& Leliwa, 2019).} The technology comprises a combination
of symbolic and statistical methods, where each statistical component
(e.g., a deep learning model) is governed by a symbolic component
utilizing a variety of natural language processing methods (e.g.,
tokenization, syntactic parsing, etc.). Symbolic components are used to
determine if a potentially abusive utterance is not a part of a broader
utterance indicating that the first one should not be considered
abusive. For example, an utterance ``you are an idiot'' is potentially
abusive, but in reality it is not, if it appears as a part of some broader context
such as ``I cannot believe he said you are an idiot.'' Another
example of using symbolic components is determining if an abusive phrase
is targeted against an interlocutor (e.g.~using a linking verb to assign
the abusive phrase with a second person as in the ``you are an idiot''
example).

Samurai has already been applied in a variety of studies, including suicidal text detection \citep{ijerph182211759}, detection of toxic usernames \citep{URBANIAK2022107371}, and detection of personal attacks on Reddit \citep{urbaniak2022personal}. For the  research presented in this paper we used the module of the system developed for the detection of personal attacks.

\textit{Personal attacks} are defined as any
kind of abusive remark made in relation to a person
(\textit{ad hominem}) rather than to the content of the argument
expressed by that person in a discussion. The definition of `personal
attack' subsumes the use of specific terms which compare other people to
animals or objects or making nasty insinuations without providing
evidence. Three examples of typical personal attacks are as follows:

\begin{itemize} 
\item \emph{You are legit mentally retarded homie.}
\item \emph {Eat a bag of dicks, fuckstick.}
\item \emph {Fuck off with your sensitivity you douche.} 
\end{itemize}

Figure \ref{fig:samuraiexample} illustrates how an  input text (such as ``ccant
believ he sad ur an id10+\ldots!'') is processed step-by-step utilizing
both statistical and symbolic methods. The performance of Samurai has been measured on a number of occasions and evaluated as sufficiently reliable for practical use \citep{ptaszynski2018cyberbullying,ijerph182211759,urbaniak2022personal,URBANIAK2022107371}.

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{example.eps}
    \caption{Example of processing of one sentence by the applied Samurai technology.}
    \label{fig:samuraiexample}
\end{figure}

% In practice, this means that a whole variety of constructions can be
% detected without the need to construct a fixed list of dictionary words
% defined \textit{a priori}. Due to utilizing symbolic components that
% oversee statistical components, \{\textsf Samurai\} recognizes complex
% linguistic phenomena (such as indirect speech, rhetorical figures or
% counter-factual expressions) to distinguish personal attacks from normal
% communication, greatly reducing the number of false alarms as compared
% to others systems used for violence detection. An example of a comparison \todo{of what with what}
% can be seen in Figure \ref{fig:samuraiexample}, and a full benchmark was
% presented in (Ptaszyński et al., 2018).

% The detection models utilized in this research were designed to detect
% personal attacks targeted against a second person (e.g.~interlocutor,
% original author of a post) and a third person/group (e.g., other
% participants in the conversation, people not involved in the
% conversation, social groups, professional groups), except for public figures
% (e.g.~politicians, celebrities). With regards to the symbolic component of
% the system, by ``models'' we mean separate rules (such as, specifying a
% candidate for the presence of personal attack, such as the aggressive
% word ``idiot,'' which is further disambiguated with a syntactic rule of
% citation, e.g., ``{[}he\(\vert\)she\(\vert\)they{]} said {[}SUBJECT{]}
% {[}PREDICATE{]}'') or sets of rules, as seen in Figure
% \ref{fig:samuraiexample}, e.g.~normalization model contains rules for
% transcription normalization, citation detection model contains rules for
% citation, etc. With regards to the statistical component, by ``models''
% we refer to machine learning models trained on large data to classify an
% entry into one of the categories (e.g., true personal attack, or false
% positive) \todo{this doesn't make sense, Rafals comment}.

% Moreover, the symbolic component of the system uses two types of
% symbolic rules, namely ``narrow rules'' and ``wide rules.'' The former
% have smaller coverage (e.g., are triggered less often), but detect
% messages containing personal attacks with high
% a precision.\footnote{Precision is defined traditionally as the ratio of correctly detected instances among all detected instances.}
% The latter have wider coverage, but their precision is lower. We
% decided to set apart the ``narrow'' and ``wide'' subgroups of the
% detection models in order to increase the granularity of the analysis.
% Firstly, we took only the detection models designed to detect personal
% attacks targeted against second person. Secondly, we used these models
% on a dataset of 320,000 Reddit comments collected on 2019/05/06.
% Thirdly, we randomly picked at most hundred returned results for each
% low-level
% model\footnote{Low-level models are responsible for detecting low-level categories. Similarly, mid-level models detect mid-level categories, by combining several low-level models, etc.}
% (some models are triggered very often while others rarely, so using all
% instances would create too much bias). There were 390 low-level models
% but many of them returned less than 100 results. We verified them
% manually with the help of expert annotators trained in detection of
% personal attacks and selected only those models that achieved at least
% 90\% of precision. The models with fewer than 100 results were
% excluded from the selection. After this step, the ``narrow'' subgroup
% contained 43 out of 390 low-level models. Finally, we tested all of the
% ``narrow'' models on a large dataset of 477,851 Reddit comments
% collected between 2019/06/01 and 2019/08/31 from two subreddits
% (r/MensRights and r/TooAfraidToAsk). Each result of the ``narrow''
% models was verified manually by a trained annotator and the ``narrow''
% models collectively achieved the precision of 93.3\%. We also tested
% the rest of the ``wide'' models on random samples of 100 results for
% each model (from the previous dataset of 320,000 Reddit comments) and we
% excluded the models that achieved less than 80\% precision. The models
% with fewer than 100 results were not excluded from the ``wide'' group.
% In this simple setup we detected 24,251 texts containing ``wide''
% attacks, where:

% \begin{itemize}
% \item  5,717 (23.6\%) contained personal attacks against second person detected by the "narrow" models,
% \item  8,837 (36.4\%) contained personal attacks against second person detected by "wide" models
% % the models other than "narrow",
% \item  10,023 (41.3\%) contained personal attacks against third persons / groups.
% The sum exceeds 100\% because some of the comments contained personal attacks against both second person and third person / groups. For example, a comment ``Fu$\ast\ast$ you a$\ast\ast$hole, you know that girls from this school are real bit$\ast\ast$es" contains both types of personal attack.
% \end{itemize}
% \todo{table with recall precision tests - Rafals comment}
